### 2017-08-17 README.Rmd
update README

- Install the most recent _stable release_:
  `devtools::install_github("benkeser/drtmle")`

- To contribute, install the _development version_:
  `devtools::install_github("benkeser/drtmle", ref = "develop")`

>>>>

Install the current stable release from
[CRAN](https://cran.r-project.org/) via

```{r cran-installation, eval = FALSE}
install.packages("drtmle")
```

A developmental release may be installed from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/) with:

```{r gh-installation, eval = FALSE}
devtools::install_github("benkeser/drtmle")
```
